

```{r}
library(plyr)
library(dplyr)
library(tidyr)
library(tidyverse)

```


Clean up company names column so they are all identical and lower case(Is there a faster way to do this?):

```{r}

refine$company <- revalue(refine$company, c(
"phillipS" = "philips"))

refine$company <- revalue(refine$company, c(
"Phillips" = "philips"))

refine$company <- revalue(refine$company, c(
"phillips" = "philips"))

refine$company <- revalue(refine$company, c(
"phllips" = "philips"))

refine$company <- revalue(refine$company, c(
"phillps" = "philips"))

refine$company <- revalue(refine$company, c(
"fillips" = "philips"))

refine$company <- revalue(refine$company, c(
"phlips" = "philips"))

refine$company <- revalue(refine$company, c(
"Akzo" = "akzo"))

refine$company <- revalue(refine$company, c(
"AKZO" = "akzo"))

refine$company <- revalue(refine$company, c(
"akz0" = "akzo"))

refine$company <- revalue(refine$company, c(
"ak zo" = "akzo"))

refine$company <- revalue(refine$company, c(
"Van Houten" = "van houten"))

refine$company <- revalue(refine$company, c(
"van Houten" = "van houten"))

refine$company <- revalue(refine$company, c(
"Van Houten" = "van houten"))

refine$company <- revalue(refine$company, c(
"unilver" = "unilever"))

refine$company <- revalue(refine$company, c(
"Unilever" = "unilever"))

```

Separate product number into two colums:


```{r}



refine %>%
  separate('Product code / number', (c('product_code', 'product_number')))

```

 Add Column with Product Categories based on the "product_code" variable I have just created. But when I try anything with product_code, an error shows: "product-code" not found.


```{r}
codes <- c("p", "x", "v", "q")
replacements <- c("Smartphone", "Laptop", "TV", "Tablet")

refine %>%
  select('product_code')

```
%>%
  mutate(if ('product_code' == "x"){product_category = "Laptop"},
                    if ('product_code' == "v"){product_category = "TV"},
                    if ('product_code' == "q"){product_category = "Tablet"})
glimpse(refine)
```










